\chapter*{\rm \large \bf REFERENCES}
\vspace{4.0mm}
\setlength{\parindent}{1cm} 

\scriptsize{}
\begin{enumerate}
    \item Mitchell, Ross; Young, Travas; Bachleda, Bellamie;
Karchmer, Michael (2006). "How Many People Use ASL in
the United States?: Why Estimates Need Updating" (PDF).
Sign Language Studies (Gallaudet University Press.) 6 (3).
ISSN 0302-1475. Retrieved November 27, 2012.

    \item Singha, J. and Das, K. “Hand Gesture Recognition Based on
Karhunen-Loeve Transform”, Mobile and Embedded
232
Technology International Conference (MECON), January
17-18, 2013, India. 365-371.

    \item D. Aryanie, Y. Heryadi. American Sign Language-Based
Finger-spelling Recognition using k-Nearest Neighbors
Classifier. 3rd International Conference on Information and
Communication Technology (2015) 533-536.

    \item R. Sharma et al. Recognition of Single Handed Sign
Language Gestures using Contour Tracing descriptor.
Proceedings of the World Congress on Engineering 2013
Vol. II, WCE 2013, July 3 - 5, 2013, London, U.K

    \item T.Starner and A. Pentland. Real-Time American Sign
Language Recognition from Video Using Hidden
Markov Models. Computational Imaging and Vision, 9(1);
227-243, 1997.e

    \item M. Jeballi et al. Extension of Hidden Markov Model for
Recognizing Large Vocabulary of Sign Language.
International Journal of Artificial Intelligence &
Applications 4(2); 35-42, 2013

    \item P. Mekala et al. Real-time Sign Language Recognition
based on Neural Network Architecture. System Theory
(SSST), 2011 IEEE 43rd Southeastern Symposium 14-16
March 2011.

    \item Y.F. Admasu, and K. Raimond, Ethiopian Sign Language
Recognition Using Artificial Neural Network. 10th
International Conference on Intelligent Systems Design and
Applications, 2010. 995-1000.

    \item J. Atwood, M. Eicholtz, and J. Farrell. American Sign
Language Recognition System. Artificial Intelligence and
Machine Learning for Engineering Design. Dept. of
Mechanical Engineering, Carnegie Mellon University,
2012.

    \item L. Pigou et al. Sign Language Recognition Using
Convolutional Neural Networks. European Conference on
Computer Vision 6-12 September 2014

    \item   Lifeprint.com. American Sign Language (ASL) Manual
Alphabet (fingerspelling) 2007.

\end{enumerate}


\newpage
